---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

require("webshot")
```

# gt-tips

<!-- badges: start -->
<!-- badges: end -->

The goal of gt-tips is to demo of some tips for `gt` table production

Features I need in a table:
  - customized calculations (e.g., break out into my own calcs)
  - readable column and row labels
  - formatting values to e.g., dollars, percent, comma
  - borders, shading, bold
  - column spanners
  - row spanners

Output formats:
  - Nice preview look
  - Something git-trackable (e.g., csv or md output)
  - Document production output (e.g., to word docs or indesign)


```{r data}
source("gtcars-ex.R")
source("tab_style.R")
head(comparison_data)
```

Here is the gt table:

```{r gt}
gttbl <- comparison_data %>%
  gt(
    rowname_col = "row_label",
    groupname_col = "grp"
  ) %>%
  cols_hide(c(mfr, model, bdy_style)) %>%
  
  # labels
  tab_stubhead("Vehicle") %>%
  tab_spanner(label = "Power", columns = c(hp, trq)) %>%
  tab_spanner(label = "Miles-per-gallon", columns = c(mpg_c, mpg_h)) %>%
  cols_label(!!! col_disp_labels) %>%
  cols_label(trq = html("Torque<br>(lb-ft)")) %>%
  
  # cell formatting
  fmt_number(columns = where(is.numeric), n_sigfig = 2) %>%
  #fmt_markdown(columns = c(grp)) %>% # currently not possible to format stub as markdown: https://github.com/rstudio/gt/issues/694
  tab_style_blue()

gtsave(gttbl, "figs/gtcars-ex.png")

```


